Efficient ancestry and mutation simulation with msprime 1.0

### 2021-11-19 paper.tex
Update table

\begin{table}
{ % begin box to localize effect of arraystretch change
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{lp{12cm}}
Interface
& Separation of ancestry and mutation simulations. Integration
with forward simulators such as \SLiM\ and \fwdpy.
Ability to store arbitrary metadata along with simulation
results, and automatic recording of provenance information
for reproducibility.
Rich suite of analytical and visualisation methods via \tskit\ library. \\

Ancestry
& SMC, SMC', Beta- and Dirac-coalescent, discrete time Wright-Fisher,
  and selective sweep models. Instantaneous bottlenecks.
  Discrete or continuous genomic coordinates, arbitary ploidy,
  gene conversion.
  Recording full ARG, full migration history, census
  events.  More efficient for large numbers of populations.\\

>>>>

\begin{table}
{ % begin box to localize effect of arraystretch change
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{lp{12cm}}
Interface
& Separation of ancestry and mutation simulations.
Ability to store arbitrary metadata along with simulation
results, and automatic recording of provenance information
for reproducibility.
Jupyter notebook~\citep{kluyver2016jupyter} integration.
Rich suite of analytical and visualisation methods via \tskit\ library. \\

Ancestry
& SMC, SMC', Beta- and Dirac-coalescent, discrete time Wright-Fisher,
and selective sweep models. Instantaneous bottlenecks.
Discrete or continuous genomic coordinates, arbitary ploidy,
gene conversion.
Output full ARG with recombination nodes, ARG likelihood calculations.
Record full migration history and census
events.  Improved performance for large numbers of populations.
Integration with forward simulators such as \SLiM\ and \fwdpy\
(``recapitation'').
\\
